\LARGE \textbf{Constrained Geometric Attitude Control on \( \SO \)}

### 2017-01-10 manuscript.tex
Clear up neighborhood discussion

%To show~\cref{item:prop_crit} we note that \( A(R) \) is a positive definite function about \( R = R_d\), with \( \Psi(R_d) = A(R_d) = 0 \).
%As a result, there exists a neighborhood \(  U \) about \( R = R_d \) such that
%\begin{align*}
%  A(R) \geq A(R_d) \; \forall \; R \in U .
%\end{align*}
%Since the desired attitude, \( R_d \), must lie in the feasible set, i.e., \( r^T R^T v < \cos \theta \), the addition of the repulsive barrier function, \( B \), does not change the minimum value of \( \Psi \).
We show~\cref{item:prop_psi_quadratic} by computing the hessian of \( \Psi \), namely \( \Hess(\Psi) \),  using the chain rule as 
\begin{align*}
    \Hess &(\Psi)\cdot (\delta R,\delta R)= (\mathbf{D}_R\parenth{\mathbf{D}_R A \cdot \delta R}\cdot \delta R) B\\
    & + \parenth{\dirDiff{A}{R} }\parenth{\dirDiff{B}{R}} 
    + \parenth{\dirDiff{B}{R} }\parenth{\dirDiff{A}{R}}\\ &+(\mathbf{D}_R\parenth{\mathbf{D}_R B \cdot \delta R}\cdot \delta R) A.
\end{align*}
The first order derivative of \( A(R) \) and \( B(R) \) are given by~\cref{eqn:eRA,eqn:eRB}. 
The hessian of \( A(R) \) is computed as 
\begin{align*}
    \dirDiff{\parenth{\dirDiff{A}{R}}}{R} &= \eta \cdot \frac{1}{2}\parenth{G R_d^T \delta R - \delta R^T R_d G}^\vee , \\
    &= \eta \cdot \frac{1}{2} \parenth{G R_d^T R \hat \eta + \hat \eta R^T R_d G}^\vee,\\
    &= \eta \cdot \frac{1}{2} \bracket{\parenth{\braces{\tr{R^T R_d G} I - R^T R_d G} \eta}^\wedge}^\vee , \\
    &= \eta \cdot \frac{1}{2} \parenth{\tr{R^T R_d G} I - R^T R_d G}\eta ,
\end{align*}
where we used the scalar triple product rule, from~\cref{eqn:STP}, to arrive at the final form.
The hessian of \( B(R) \) is computed as
\begin{align*}
    \dirDiff{\parenth{\dirDiff{B}{R}}}{R} =& \eta \cdot \left[\frac{\parenth{\delta R^T v}^\wedge r}{\alpha\parenth{r^T R^T v - \cos \theta}} \right. \\
    & \left. - \frac{\parenth{R^T v}^\wedge r \parenth{r^T \delta R^T v}}{\alpha \parenth{r^TR^Tv - \cos \theta}^2}   \right] .
\end{align*}
The term \( \parenth{\delta R^T v}^\wedge r\) is simplified as
\begin{align*}
    \parenth{\delta R^T v}^\wedge r &= - \hat{r} \delta R ^T v , \\
    &= - \hat{r} \parenth{R \hat \eta}^T v , \\
    &= \hat{r} \parenth{\hat{\eta} R^T } v , \\
    &= - \hat{r} \parenth{R^T v}^\wedge \eta ,
\end{align*}
where we utilized the hat map property from~\cref{eqn:cross_product}.
Similarly, the term \( r^T \delta R^T v \) is simplified as
\begin{align*}
    r^T \delta R^T v &= r^T \parenth{-\hat \eta R^T}v , \\
    &= r^T \parenth{R^T v}^\wedge \eta .
\end{align*}
The hessian of \( B(R) \) then becomes
\begin{align*}
    \dirDiff{\parenth{\dirDiff{B}{R}}}{R} =& \eta \cdot \left[ - \frac{ \hat r \parenth{R^T v}^\wedge}{\alpha \parenth{r^T R^T v - \cos \theta}} \right. \\ 
    & \left. - \frac{\parenth{R^T v}^\wedge r r^T \parenth{R^T v}^\wedge }{ \alpha\parenth{r^T R^T v - \cos \theta}^2}  \right] \eta .
\end{align*}
Using these terms, we evaluate \( \Hess{\Psi} \) at the desired attitude \( R = R_d \) as follows. Since $A=0$ and $\mathbf{D}_R A=0$ at $R=R_d$, 
\begin{align*}
    \Hess(\Psi)\cdot (\delta R,\delta R)\big|_{R=R_d} = \eta \cdot \frac{1}{2} B \parenth{\tr{G}I -  G} \eta , 
\end{align*}
which is positive definite since \( B > 1\) and \( \sum g_i > g_i\). 
The domain \( D \) is an open neighborhood of the desired attitude \( R_d \).
More explicitly, the set \( D \) of the metric space \( \parenth{R \in \SO, \Psi(R,R_d)} \) is an open neighborhood of \( R_d \) if there exists an \( \epsilon > 0 \) such that for any \( R \in \SO | \Psi(R,R_d) < \epsilon \), it is also true that \( R \in D \).
We can ensure that \( D \) is an open neighborhood of \( R_d \) by choosing \( \epsilon = \min \braces{\psi, \Psi(R|r^T R^T v = \beta,R_d)}\).
The selected domain \( D \) excludes the undesired equilibrium points of \( A(R) \) and the infeasible regions defined by the constraints \( r^T R^T v_i \), i.e. the desired attitude should be sufficiently far away from the constraints. 
The single equilibrium point occurs at \( R=R_d\) and results in \( e_R = 0 \) and \( \Psi = A = 0\).
Therefore, in \( D \) the configuration error function is quadratic and the bounds in~\cref{item:prop_psi_quadratic} are valid~\cite[Proposition 6.30]{bullo2004}.

>>>>

%To show~\cref{item:prop_crit} we note that \( A(R) \) is a positive definite function about \( R = R_d\), with \( \Psi(R_d) = A(R_d) = 0 \).
%As a result, there exists a neighborhood \(  U \) about \( R = R_d \) such that
%\begin{align*}
%  A(R) \geq A(R_d) \; \forall \; R \in U .
%\end{align*}
%Since the desired attitude, \( R_d \), must lie in the feasible set, i.e., \( r^T R^T v < \cos \theta \), the addition of the repulsive barrier function, \( B \), does not change the minimum value of \( \Psi \).
We show~\cref{item:prop_psi_quadratic} by computing the hessian of \( \Psi \), namely \( \Hess(\Psi) \),  using the chain rule as 
\begin{align*}
    \Hess &(\Psi)\cdot (\delta R,\delta R)= (\mathbf{D}_R\parenth{\mathbf{D}_R A \cdot \delta R}\cdot \delta R) B\\
    & + \parenth{\dirDiff{A}{R} }\parenth{\dirDiff{B}{R}} 
    + \parenth{\dirDiff{B}{R} }\parenth{\dirDiff{A}{R}}\\ &+(\mathbf{D}_R\parenth{\mathbf{D}_R B \cdot \delta R}\cdot \delta R) A.
\end{align*}
The first order derivative of \( A(R) \) and \( B(R) \) are given by~\cref{eqn:eRA,eqn:eRB}. 
The hessian of \( A(R) \) is computed as 
\begin{align*}
    \dirDiff{\parenth{\dirDiff{A}{R}}}{R} &= \eta \cdot \frac{1}{2}\parenth{G R_d^T \delta R - \delta R^T R_d G}^\vee , \\
    &= \eta \cdot \frac{1}{2} \parenth{G R_d^T R \hat \eta + \hat \eta R^T R_d G}^\vee,\\
    &= \eta \cdot \frac{1}{2} \bracket{\parenth{\braces{\tr{R^T R_d G} I - R^T R_d G} \eta}^\wedge}^\vee , \\
    &= \eta \cdot \frac{1}{2} \parenth{\tr{R^T R_d G} I - R^T R_d G}\eta ,
\end{align*}
where we used the scalar triple product rule, from~\cref{eqn:STP}, to arrive at the final form.
The hessian of \( B(R) \) is computed as
\begin{align*}
    \dirDiff{\parenth{\dirDiff{B}{R}}}{R} =& \eta \cdot \left[\frac{\parenth{\delta R^T v}^\wedge r}{\alpha\parenth{r^T R^T v - \cos \theta}} \right. \\
    & \left. - \frac{\parenth{R^T v}^\wedge r \parenth{r^T \delta R^T v}}{\alpha \parenth{r^TR^Tv - \cos \theta}^2}   \right] .
\end{align*}
The term \( \parenth{\delta R^T v}^\wedge r\) is simplified as
\begin{align*}
    \parenth{\delta R^T v}^\wedge r &= - \hat{r} \delta R ^T v , \\
    &= - \hat{r} \parenth{R \hat \eta}^T v , \\
    &= \hat{r} \parenth{\hat{\eta} R^T } v , \\
    &= - \hat{r} \parenth{R^T v}^\wedge \eta ,
\end{align*}
where we utilized the hat map property from~\cref{eqn:cross_product}.
Similarly, the term \( r^T \delta R^T v \) is simplified as
\begin{align*}
    r^T \delta R^T v &= r^T \parenth{-\hat \eta R^T}v , \\
    &= r^T \parenth{R^T v}^\wedge \eta .
\end{align*}
The hessian of \( B(R) \) then becomes
\begin{align*}
    \dirDiff{\parenth{\dirDiff{B}{R}}}{R} =& \eta \cdot \left[ - \frac{ \hat r \parenth{R^T v}^\wedge}{\alpha \parenth{r^T R^T v - \cos \theta}} \right. \\ 
    & \left. - \frac{\parenth{R^T v}^\wedge r r^T \parenth{R^T v}^\wedge }{ \alpha\parenth{r^T R^T v - \cos \theta}^2}  \right] \eta .
\end{align*}
Using these terms, we evaluate \( \Hess{\Psi} \) at the desired attitude \( R = R_d \) as follows. Since $A=0$ and $\mathbf{D}_R A=0$ at $R=R_d$, 
\begin{align*}
    \Hess(\Psi)\cdot (\delta R,\delta R)\big|_{R=R_d} = \eta \cdot \frac{1}{2} B \parenth{\tr{G}I -  G} \eta , 
\end{align*}
which is positive definite since \( B > 1\) and \( \sum g_i > g_i\). 
The domain \( D \) is an open neighborhood of the desired attitude \( R_d \).
The selected domain \( D \) excludes the undesired equilibrium points of \( A(R) \) and the infeasible regions defined by the constraints \( r^T R^T v_i \), i.e. the desired attitude should be sufficiently far away from the constraints. 
As a result, the single equilibrium point in \( D \)occurs at \( R=R_d\) and results in \( e_R = 0 \) and \( \Psi = A = 0\).
Therefore, in \( D \) the configuration error function is quadratic and the bounds in~\cref{item:prop_psi_quadratic} are valid~\cite[Proposition 6.30]{bullo2004}.
